\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{YAO LONG TAN} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+65 8588 8968 \\ Singapore, Singapore} 
\address{\href{mailto:yaolong.tan.2021@scis.smu.edu.sg}{yaolong.tan.2021@scis.smu.edu.sg} \\ \href{https://linkedin.com/in/yaolongt}{linkedin.com/in/yaolongt} \\ \href{https://github.com/yaolongt}{github.com/yaolongt}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	DESCRIPTION
%----------------------------------------------------------------------------------------
\vspace{-1.25em}
\begin{rSection}{About Me}

Enthusiastic, Diligent, Motivated. Student pursuing Computer Science at Singapore Management University aspiring to be Software Engineer. Seeking internship opportunities in development and cloud computing to make a positive impact.

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION	
%----------------------------------------------------------------------------------------
\vspace{-0.25em}
\begin{rSection}{EXPERIENCE}
\textbf{Full-stack Software Engineer Intern}, Vibefam \hfill Jan 2023 - July 2023\\
 \vspace{-1.5em}
 \begin{itemize}
    \itemsep -5pt {} 
     \item {Spearheaded the development of a feature, Marketing Campaign Performance, from scratch and justified design structures.}
     \item {Successfully resolved several bugs to ensure product stability, and enhancing user experience.}
     \item {Developed modular, robust code to ensure cleanliness and re-usability, with a focus on self-documentation.}
     \item {Wrote comprehensive tests to ensure code reliability and robustness, maintaining a bug-free environment.}
     \item {Conceptualized and articulated the design of a frontend component to ensure consistency across the product.}
 \end{itemize}

\vspace{-0.25em}
\textbf{Student Assistant (Special Projects)}, SMU Academy \hfill Sep 2023 - Dec 2023\\
 \vspace{-1.5em}
 \begin{itemize}
    \itemsep -5pt {} 
     \item {Engineered Python code enhancements to streamline the team's workflow efficiency.}
     \item {Created a fundamental Python programming curriculum for team introduction, focusing on clarity and understanding.}
 \end{itemize}
 
\vspace{-0.25em}
\textbf{Full-stack Software Engineer Intern}, Azendian Solution \hfill May 2023 - Aug 2023\\
 \vspace{-1.5em}
 \begin{itemize}
    \itemsep -5pt {} 
     \item {Designed and developed a robust and scalable backend with REST APIs for dashboard used in Keppel's Cooling District}
     \item {Utilized Git and JIRA for effective communication and justify design decisions to colleagues and superiors.}
 \end{itemize}
 
\vspace{-0.25em}
\textbf{Administrator}, Top Taekwondo Academy \hfill May 2021 - May 2022\\
 \vspace{-1.5em}
 \begin{itemize}
    \itemsep -5pt {} 
     \item {Managed daily admin tasks using spreadsheets. Spearheaded design for marketing collaterals using Figma and Canva.}
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{Grab Calling System, FYP} {An in-house call solution for Grab super-app, to replace incumbent, outsourced solution. Utilized frameworks like LiveKit and WebRTC technology, we developed a mobile app using Kotlin with a better call reliability and stability. Additional features includes post-call transcription and sentiment analysis.
\href{https://drive.google.com/file/d/1y8UnuO__RFND29A64KiiEDGlcCrKM5JP/view?usp=sharing}{(Slides)} \href{https://drive.google.com/file/d/1GAYOGzGXRzd9tYW05xrRtNEaxdWrBHqD/view?usp=sharing}{(Poster)}}

\item \textbf{Admin Portal} {A highly available and scalable solution for admin staff to handle users and points accounts. Developed microservices in Go, Python, and NextJS. Utilised AWS Serverless architecture to enable robust system.
\href{https://drive.google.com/file/d/1oLYaHGlfMH5x33raus1Ed0TU9uiwzNIl/view?usp=share_link}{(Demo)} \href{https://github.com/cs301-2023-g3t3}{(Repository)}}

\item \textbf{Sysadmin Platform, Cob} {Dedicated platform for system administration challenges, inspired by LeetCode. Developed microservices in Go and Python that are integral part of the system. Utilised RabbitMQ, Kubernetes, Helm, and Tilt. \href{https://drive.google.com/file/d/1tmAqFLv3bauuZyU5m-ULxpX706uy0BL6/view?usp=share_link}{(Slides)}}

\item \textbf{Carpooling App, Bussin} {A carpooling app service that leverages on private car efficiency and seamlessly integrated public transport options that tries to mitigate traffic congestion. Developed backend RESTful API microservice using Spring. Awarded Credit Suisse Outstanding Award.}

\item \textbf{Android Game, Dartero} {Developed an Android game using Java, utilizing multithreading and concurrency. \href{https://github.com/DarteroGame/Dartero}{(Repository)}}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\vspace{-1.25em}

\item \textbf{Languages}: {Java, Python, JavaScript/Typescript, Go, Kotlin}
\item \textbf{Frameworks}: {Node, Express, Gin, Spring, React, Vue}
\item \textbf{Database}: {MySQL, PostgreSQL, MongoDB, Firebase}
\item \textbf{Technologies}: {Docker, AWS, Git, Jira, Figma, Canva, Premiere Pro, Photoshop, Firebase Cloud, LiveKit, WebRTC}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Bachelor of Science, Computer Science}, Singapore Management University \hfill {Expected 2025}\\
Relevant Coursework: Data Structures and Algorithm, Object Oriented Programming, Software Development, Database, Operating System, Cloud Engineering, DevOps

{\bf Diploma in Engineering, Computer Engineering}, Singapore Polytechnic \hfill {2018 - 2012}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Activities} 
\vspace{-1.25em}

\item \textbf{Honorary General Secretary, SMU Whitehat Society} {Provided comprehensive administrative support to the club, encompassing tasks such as crafting email messages, compiling records for official documentation, and generated meeting minutes.}

\item \textbf{Quarter Master/Exco, SP International Students' Club} {Meticulously oversee the management of club properties and maintain a consistently tidy club room environment. Chairperson for the International Students' Freshmen Orientation Program, leading the strategic planning and meticulous execution of the program's activities. Executed over 12 events successfully.}

\end{rSection}


\end{document}